---
title: "Assignment1R"
author: "Nompumelelo Ndlovu"
date: "17/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.1 Variables


# What is the value of " B " after running these command?

```{r}
a <- 5.0
c <- 10
t <- 12
B <- a+c/t
```

The value of B is 5.83333333333333


# What type of vector do you get in each of the following?

```{r}
vec_1 <- c(44, 5, 0, "k")
```


 The type of vector represented above is an integer and character vector

```{r}
vec_2 <- c(1, 2, 3, FALSE)
```

 The type of vector represented above is a numerical and logical vector

```{r}
vec_3 <- c("a", "b", "c", TRUE)
```

 The type of vector represented above is a character and logical vector 

```{r}
vec_4 <- c(1, 2, 3, "4")
```

The type of vector represented above is a numerical vector 

# 1.2 Conditional Subsetting 
Consider the following vector
```{r}

vec <- c(141.2741, 141.8392, 140.5730,NA, 141.3571, 139.8689, 
         137.9384, NA,139.6620, 138.2521, 138.8635, 141.3885, NA)
```

# 1.2.1 Create a vector vec_1 with no missing values using conditional subsetting and explain your code 

vec <- c(141.2, 141.8392, 140.5730,NA, 141.3571, 139.8689, 
         137.9384, NA,139.6620, 138.2521, 138.8635, 141.3885, NA)
         
print( na.omit(vec) )




