---
title: "Assignment1R"
author: "Nompumelelo Ndlovu"
date: "17/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1.1 Variables


# What is the value of " B " after running these command?

```{r}
a <- 5.0
c <- 10
t <- 12
B <- a+c/t
```

The value of B is 5.83333333333333


# What type of vector do you get in each of the following?

```{r}
vec_1 <- c(44, 5, 0, "k")
```


 The type of vector represented above is an integer and character vector

```{r}
vec_2 <- c(1, 2, 3, FALSE)
```

 The type of vector represented above is a numerical and logical vector

```{r}
vec_3 <- c("a", "b", "c", TRUE)
```

 The type of vector represented above is a character and logical vector 

```{r}
vec_4 <- c(1, 2, 3, "4")
```

The type of vector represented above is a numerical vector 

# 1.2 Conditional Subsetting 
Consider the following vector
```{r}

vec <- c(141.2741, 141.8392, 140.5730,NA, 141.3571, 139.8689, 
         137.9384, NA,139.6620, 138.2521, 138.8635, 141.3885, NA)
```

# 1.2.1 Create a vector vec_1 with no missing values using conditional subsetting and explain your code 

```{r}
vec_11 <- c(141.2, 141.8392, 140.5730,NA, 141.3571, 139.8689, 
         137.9384, NA,139.6620, 138.2521, 138.8635, 141.3885, NA)
         
 print( na.omit(vec_11) )        
```

 
The code will run and it will print the values with all the missing values removed.

# 1.2.2. Create a vector of indexes of missing values using conditional subsetting and explain your code. 


```{r}
missingvals<- (is.na(vec_11))
```
The code will run and return true for values that are missing and false for values that exist



# 1.2.3. Write a code to determine how many missing values are in vec.
```{r}
print (sum(is.na(vec_11)))
```



# 1.2.4. Write a R code to create a data frame which contains details of 3 students as follows:
# Name , surname, age and gender 

```{r}
students= data.frame(Name= c("Kamogelo", "Kitso", "Hamilton"),Surname= c("Mothibedi", "Baranye", "Gabadise"), Gender= c("Female", "Female" , "Male"),Age=c(19,18,20) )

print(students)

```

# 2. Functions in R
# 2.1. Create a function which returns a mean of an input vector and explain your code

```{r}
x <- c(12,14,28,34)
mean(x)

```

x is the input vector and "mean(x)" is a function that calculates and returns the value of the mean.

# 2.2. Create a function which take no inputs , it reads a Titanic .csv file and returns its content and explain your code.

read.csv(Titanic)

- The function will read and output the data that is in the data set file 


#3. Conditionals and Loops 
#3.1. Write a function that take an input below and returns a transformed vector below into 1 when its element is male and 2 when its female using ifelse. 

```{r}
g <- c("MALE","FEMALE","FEMALE","MALE","FEMALE","MALE","MALE","FEMALE", "MALE","MALE","FEMALE","MALE","MALE",
"FEMALE","MALE","MALE","MALE")
g <- c("MALE","FEMALE","FEMALE","MALE","FEMALE","MALE","MALE","FEMALE", "MALE","MALE","FEMALE","MALE","MALE",
       "FEMALE","MALE","MALE","MALE")
gg_Sex <- function(x){
  ifelse(x == "MALE",1,2)
}
gg_Sex <- gg_Sex(g)

 

gg_Sex

```
# 3.2. Generate x from normal distribution and sample with replacement "M" and "F" for male and female respectively by running the code below.

```{r}
x <- rnorm(1000, 120, 5)
y <- sample(c("M","F"),size = 1000, replace = TRUE)


```
# 3.2.1. Use the "cbind " function in R to create one dataset and assign it to df 
```{r}
x <- rnorm(1000, 120, 5)
y <- sample(c("M","F"),size = 1000, replace = TRUE)
df <- cbind(x,y)
```
# 3.2.2. Convert df from 3.2.1 into a data.frame

```{r}
x <- rnorm(1000, 120, 5)
y <- sample(c("M","F"),size = 1000, replace = TRUE)
df <- data.frame(cbind(x,y))
```
# 3.2.3. Write a code using tidyverse to compute a number of males ("M") and females ("F") in 3.2.1

```{r}
x <- rnorm(1000, 120, 5)
y <- sample(c("M","F"),size = 1000, replace = TRUE)
df <-(cbind(x,y))




```
# 3.2.4. Create a bar plot using ggplot to visualize your results in 3.2.3





# 3.2.5. Use mutate function to add sum of x per "M" and "F" and plot the results using sum of x per "M" and "F"




